---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/poissonconsulting/tsdbr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/tsdbr/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/tsdbr/graph/badge.svg)](https://app.codecov.io/gh/poissonconsulting/tsdbr)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/license/mit/)
<!-- badges: end -->

# tsdbr

`tsdbr` is designed to create, populate, maintain and query SQLite databases of environmental time series data.

## Utilisation

```{r, warning=FALSE}
library(tsdbr)
conn <- ts_create_db(":memory:")
options(tsdbr.conn = conn)
ts_add_parameter("discharge", "cms")
ts_add_site("Niagara Falls")
ts_add_station("S1", "discharge", "Niagara Falls", "hour")
data <- data.frame(
  Station = "S1", DateTime = ISOdate(2000, 9, 1, 0:23),
  Recorded = 0:23 - 2,
  stringsAsFactors = FALSE
)
ts_add_data(data)
data <- ts_get_data(
  start_date = as.Date("2000-09-01"),
  end_date = as.Date("2000-09-02")
)
print(head(data))
ts_plot_data(data)
ts_disconnect_db()
```

## Installation

To install the latest version from GitHub [repository](https://github.com/poissonconsulting/tsdbr)

``` r
# install.packages("remotes")
remotes::install_github("poissonconsulting/tsdbr")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/tsdbr/issues).

[Pull requests](https://github.com/poissonconsulting/tsdbr/pulls) are always welcome.

## Code of Conduct

Please note that the tsdbr project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

