---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/poissonconsulting/tsdbr.svg?branch=master)](https://travis-ci.org/poissonconsulting/tsdbr)
[![Coverage status](https://codecov.io/gh/poissonconsulting/tsdbr/branch/master/graph/badge.svg)](https://codecov.io/github/poissonconsulting/tsdbr?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)

# tsdbr

`tsdbr` is designed to create, populate, maintain and query SQLite databases of environmental time series data.

## Utilisation

```{r, warning=FALSE}
library(tsdbr)
conn <- ts_create_db(":memory:")
options(tsdbr.conn = conn)
ts_add_parameter("discharge", "cms")
ts_add_site("Niagara Falls")
ts_add_station("S1", "discharge", "Niagara Falls", "hour")
data <- data.frame(Station = "S1", DateTime = ISOdate(2000, 9, 1, 0:23),
                   Recorded = 0:23 - 2,
                   stringsAsFactors = FALSE)
ts_add_data(data)
data <- ts_get_data(start_date = as.Date("2000-09-01"),
                    end_date = as.Date("2000-09-02"))
print(head(data))
ts_plot_data(data)
ts_disconnect_db()
```

## Installation

To install the latest version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
``` r
# install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("tsdbr")
```

To install the latest development version from [GitHub](https://github.com/poissonconsulting/tsdbr)
``` r
# install.packages("devtools")
devtools::install_github("poissonconsulting/tsdbr")
```

## Citation

```{r, comment="", echo=FALSE}
citation(package = "tsdbr")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/tsdbr/issues).

[Pull requests](https://github.com/poissonconsulting/tsdbr/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
