---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/poissonconsulting/tsdbr.svg?branch=master)](https://travis-ci.org/poissonconsulting/tsdbr)
[![Coverage status](https://codecov.io/gh/poissonconsulting/tsdbr/branch/master/graph/badge.svg)](https://codecov.io/github/poissonconsulting/tsdbr?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)

# tsdbr

tsdbr provide functions to create, populate, maintain and query an SQLite database of environmental time series data.

tsdbr is designed to be simple to use with minimal dependencies and maximal database integrity independence.

## Installation

To install the latest version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
``` r
# install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("tsdbr")
```

To install the latest development version from [GitHub](https://github.com/poissonconsulting/tsdbr)
``` r
# install.packages("devtools")
devtools::install_github("poissonconsulting/tsdbr")
```

## Citation

```{r, comment="", echo=FALSE}
citation(package = "tsdbr")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/tsdbr/issues).

[Pull requests](https://github.com/poissonconsulting/tsdbr/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
